\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, verse, fullpage, pslatex, savetrees, boxedminipage}

\title{Awaken the Nightwalker}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle

\begin{center}
\end{center}

\begin{verse}
Sleep, sometimes friend, sometimes enemy, \\
I cast you away. \\
No more long deep slumber, \\
No more hoping for rest\\
When I know I can have none. \\
Sleep, my nightly shadow,\\
I take my leave of you.\\
Time has come for the long night's ending\\
Time has come for the Nightwalker's Awakening.

Sleep, lord of the night, embracer of darkness\\
You have warmed my sunless hours\\
And cooled me against noon's vile heat.\\
Sleep, Keeper of dreams, Lord of silence.\\
Time has come to part. \\
From your gentle-firm grasp I break free.\\
From your lands of dreams, I walk away.\\
From well trod roads I stray.\\
I am the Nightwalker, \\
Traveler of unknown ways.

No more shall I pass through Oblivion's Gate.\\
No more shall I follow Sun and shun Moon.\\
No more shall sweet slumber offer \\
Blissful, ignorant reprieve.\\
My mattress and pillow I surrender.\\
My sheets and bed I despise.\\
Unconsciousness I will not allow,\\
Sleep's fortress of solitude I will abandon.\\
I am the Nightwalker,\\
Restless, tireless, unweary. 

From dawn to dusk,\\
Humanity's heartthrob surrounds me.\\
From dusk to dawn,\\
I walk alone.\\
No hand to hold, no voice to hear.\\
I surround myself with mine own.\\
Time's unyielding march,\\
Destiny's determined gait,\\
My companions two. My companions few.\\
I am the Nightwalker,\\
I walk alone. 

I sleep not, but still I dream.\\
With eyes awake, with eyes closed.\\
Dreams into reality I shape,\\
With my fingers' determined motion.\\
Each tap on plastic key, a new world unfolds.\\
From mind's hidden depths,\\
To screen's open display,\\
My dreams flow unbroken \\
I am the Nightwalker,\\
Weaver of Dreams. 

I reach ahead, but always look behind.\\
My days are now lengthened,\\
My time has now slowed.\\
But still to infinity's sword,\\
I offer only a needle.\\
To live once and then nevermore,\\
The Doom of Humble Human.\\
The river of time flows unbarred,\\
And with it I sail.\\
Forward I reach, never afraid,\\
Behind I look, never in regret.\\
I am the Nightwalker,\\
I have awoken.

\end{verse}

\begin{center}
\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}

\end{center}

\end{document}