\documentclass[12pt,letterpaper]{article}
\usepackage{setspace, verse, fullpage, pslatex}

\title{Hallucinogen Hymn\\ A research poem}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle
\begin{verse}
Greetings, people of Earth.\\
I come to you from another plane,\\
I am the Hallucinogen,\\
I am your Demon and I am your God.\\
Give me your tired, your poor,\\
Your huddled masses yearning to breathe free.\\
And I shall free them and bring them\\
To hidden lands buried deep within their souls.\\
I am the chemical confusion,\\
The artificial adoration,\\
I am the Hallucinogen.

From my three forms,\\
Sisters all,\\
Take your pick.

Psychedelic psilocybin,\\
The Firstborn.\\
Mind-manifester, soul revealer.\\
She is the Keymaker, the Opener of Doors.\\
She will whisper in your ears,\\
Only things you already know.\\
If this cold, dull world in boredom binds you,\\
Seek out the magic mushroom, the Peruvian Torch\\
or Lysergic Acid made by mortal touch.

Dissociative dextromethorphan,\\
Firstborn's companion.\\
Denier of senses, Creator of Dreams\\
She is the Guardian, she keeps the keys.\\
With the dust of Angels, and the smoke of laughter\\
She will enshroud your mind and open your eye.\\
She turns you loose.\\
But her garden is walled,\\
Walled by stone stacked by you.

Deliriant dimenhydrinate,\\
Deceiver of fools.\\
Weaver of Dreams, trickster supreme.\\
She is the Sleepwalker, Mimic of fevers.\\
Mandrake's root and nightshade's fruit\\
Fuel a psychonaut's quest.\\
Whether you seek the Heaven of Dreams\\
Or the Hell of War.\\
In her fragrant arms you find peace,\\
As her fingers ruffle your hair,\\
Erasing all your mind's cares.

Greetings, people of earth.\\
I come in peace,\\
Take me to your leader.\\
This is not the first that we have met,\\
Nor shall it be the last.\\
Shaman's tobacco,\\
God's Cocoa.\\
Warrior's rage,\\
Assassin's hashish.\\
Treehugger's dream,\\
Inquisitor's injection.\\
Behind your greatest and your least\\
My shadow has stood.

\end{verse}

\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}
\end{document}