\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, verse, fullpage, pslatex, savetrees}

\title{Jump}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle
\begin{verse}

Jump. \\
Higher, Longer, Faster, maybe Stronger. \\
Muscles contract then expand, \\
Yin and Yang, down then up. \\
Athletes jump across the field, \\
Children jump over a rope, \\
Thieves jump over a fence. 

Jump. \\
In fear and surprise.\\
Body moves as one \\
Eyes widen, eyebrows raise, \\
Adrenaline floods the blood, \\
Pupils dilate and the heart beats faster. \\
To fight or to flight, \\
That is the question.

Jump.\\
From meaning to meaning, use to use\\
Verse as my springboard,\\
Rhyme as my landing pad.

Jump.\\
From aircraft to battlefield,\\
From debate to decision,\\
Answer the bugles' call,\\
Make your choices,\\
Capture the chance.

Jump.\\
Across boundaries, real and not.\\
Break through walls by ignoring them.\\
Add a dimension, rise to the challenge, avoid the obstacles.\\
Forwards and backwards, left and right, move swift and sharp.\\
From Math to Physics, over to English and Spanish.\\
Between subjects, from interests to hobbies.

Jump.\\
Reach for the stars,\\
Send cows over the moon.\\
Heads held high, eyes focused,\\
Muscles tensed, lungs expand, then collapse.\\
Look to the future, stay rooted in the past.\\
Bend, crouch, stretch. 

Jump.\\
\end{verse}

\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}
\end{document}