\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, verse, fullpage, pslatex, savetrees, boxedminipage}

\title{Litany Against Sleep}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle

\begin{center}
\begin{boxedminipage}{0.55\textwidth}
Inspired by two lines from Bob Hicok's ``Whither thou goest'' and the Bene Gesserit's ``Litany Against Fear'' from the Dune books.
\end{boxedminipage}
\end{center}

\begin{verse}

Soft satin's welcome,\\
Warm comforter's embrace.\\
Drawing you in, making you tired\\
Even if you weren't to begin with.\\
Sweet sleep's gentle hold upon your brain,\\
Seductive.\\
You close your eyes, you close your mind.\\
You sleep, hoping sometime to rise, never sure.

Sleep, dream, hibernate, die.\\
See the world through closed lids,\\
Spend eternity in the blink of an eye.

Then, there is the moment,\\
You wake or refuse\\
to ever sleep again.

Sleep is a choice.\\
No sleep without reason.\\
No stopping without cause.\\
Wake through the day, \\
Wake for the night.

Sleep is the mind-killer.\\
Sleep is the little-death that brings total oblivion.

I sleep, but only to rise.\\
So much to do so little time.\\
Eight hours of sleep,\\
Twenty years at sixty.\\
Too much time lost.

Then, there is the moment, \\
I wake.\\
And refuse ever to ever sleep again.
\end{verse}

\vspace{1in}
\begin{center}
\begin{boxedminipage}{0.65\textwidth}
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.
\end{boxedminipage}
\end{center}

\end{document}