\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, verse, fullpage, pslatex, savetrees}

\title{Symphony in Shift-Alt-F12}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle
\begin{verse}
Keyboard, keyboard on the desk,\\ 
Where is the easiest key press?\\ 
Soft fingertip on hard keys' top,\\ 
Each strike does a letter drop.\\ 
Humble keyboard, plastic and metal\\ 
To pen and paper quite fatal.\\ 
To the rhyme of clickety-clack\\ 
I dedicate this tuneless track.

From Big Blue's corporate culture\\ 
Sprang forth a noisy creature.\\ 
Buckling spring requiring forceful push\\ 
IBM Model M makes many a users' blood rush.\\ 
Each key rings loud as metal crumples\\ 
To some unbearable, but for others\\ 
An oath swearable.\\ 
Against RSI's rampage,\\ 
This keyboard offers safe passage. 
 
Sweet Apple's flesh,\\ 
Rosy red and fresh.\\ 
Sleek and slender, spick and span\\ 
A religion for the elegant man.\\ 
No loud clack in Steve's domain,\\ 
Soft press is each key's refrain.\\ 
First plastic and glass,\\ 
Now through metal does rubber pass.\\ 
Flat and flush,\\ 
They'll make a diva blush.\\ 
Apple's keyboard, wired and without\\ 
Losing one makes a Sad Mac pout. 
 
Optimus Prime, leader of the Autobots.\\ 
Optimus Maximus, a keyboard made after too many pots.\\ 
Each key shines bright\\ 
With LED's organic light.\\ 
At eighty score and more a pop,\\ 
Your fingers on keys do consciously drop.\\ 
Keep coffee and Coke beyond the rise,\\ 
Else sparks and smoke mark this board's demise. 
 
Dell.\\ 
Simple like a church bell.\\ 
No fancy lights,\\ 
No sharp metallic bites.\\ 
Words at a dime a dozen\\ 
The price makes a college students heart lighten.\\ 
White on sable,\\ 
This one has its own fable.\\ 
There's no place like home,\\ 
And with this I'll write my tome. 
 
Keyboard, keyboard on the desk,\\ 
Who's the fastest typist of them all?\\ 
At half a word a moment, it's not my call.\\ 
100 words a minute or more,\\ 
That's what I hear from lore.\\ 
As the clicks fade and my symphony ends,\\ 
To my work my mind tends.\\ 
From quill sprung Shakespeare,\\ 
From typewriter, Twain.\\ 
Coffee table's napkin is Rowling's screen\\ 
Keyboard's bard is yet to be seen.\\ 

A hundred and four keys to press,\\ 
Many words to express,\\ 
Many more to impress.\\ 
Humble keyboard be stage and fence\\ 
To my finger's dance.\\ 
To the rhyme of clickety-clack\\ 
I dedicate this tuneless track. 
\end{verse}

\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}
\end{document}