\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, verse, fullpage, pslatex, savetrees, boxedminipage}

\title{Undefeatable}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle

\begin{center}
\begin{boxedminipage}{0.55\textwidth}
Inspired by, and borrowing elements from, the song ``Indestructible'' by Disturbed and the poem ``Invictus'' by William Ernest Henley.
\end{boxedminipage}
\end{center}

\begin{verse}
Stand tall and proud, heroes invincible.\\
Shout with one voice, strong and firm.\\
Absolutely completely indestructible. Undefeatable.

Captains of our Souls, Masters of Fate,\\
Do your duty, protect us from harm.\\
Stand tall and proud, heroes invincible.

Guardians of the Gate\\
Hold your ground, be quiet and calm.\\
Absolutely completely indestructible. Undefeatable.

Fight for the people, fight against hate.\\
Be good and just, to the innocent do no harm.\\
Stand tall and proud, heroes invincible.

Gods of War, destroyers insatiate.\\
Each swing of sword shatters shield and arm.\\
Absolutely completely indestructible. Undefeatable.

Release the fires of Hell from behind the grate.\\
Let every fallen enemy fear your terrible calm.\\
Shout with one voice, strong and firm.\\
Absolutely completely indestructible. Undefeatable.

\end{verse}

\begin{center}
\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}

\end{center}

\end{document}