\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, fullpage, pslatex}

\title{Agent Cinderella}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle
\doublespacing

\section*{Part 1}

As she swept the broom back and forth on the now spotless marble floor, her heart was pounding in her chest. The weeks of staying in deep cover in this damned house with those domineering bitches was about to pay off and it was all she could really think about. In retrospect, the mission should have failed long her ago. Who would have guessed that her ``stepmother'' and ``stepsisters'' wouldn't have noticed that the real Ella had actually been whisked away from the hospital and replaced by an almost, but not quite, look alike? Obviously someone at intel was either a certified genius or a complete lunatic, probably both.

She was snapped out of her reverie by the sharp sound of the stepmother's really expensive shoes on the marble. ``Ella, Ella'' her sharp cackle of a voice came from down the corridor, ``Where are you, you pathetic excuse of a maid? Why haven't you cleaned up the kitchen yet?''. Cinderella pushed out the thought of quietly snapping the old hag's neck in the middle of the night and instead said, as sweetly as she could ``I'm here mother. I was getting to the kitchen next.''

``Next? Next? By next do you mean next day?'' Her towering figure appeared in the doorway and she spent a full five seconds glowering at Cinderella who for her part looked demurely at the tip of her broom. ``Forget about the kitchen, you can do it later. Now go help your sisters ready for their big night, if we're late, it'll be on your head.'' ``Yes mother,'' and she shuffled away taking note of the place on her mother's neck where she wanted to land a karate chop separating adjacent vertebrae and severing the spinal cord.

Four hours and much insults and insinuations later, her ugly stepsisters were finally leaving. Cinderella thought the dresses were gaudy and cut all wrong and that they served only to amplify one's anemia and the others obesity. She pitied the poor prince and if she hadn't been under strict orders, would have done him a favor by putting a bullet through their heads (which were empty enough for one bullet to do the job for both). She watched quietly as they made a great fuss entering their carriage, the stepmother in her vampire-like purple costume in front. Cinderella had been told to put on a whole drama about putting on a dress and then watch helplessly as her sisters tore it to pieces, but she had told her handler in no uncertain terms where to put his sense of drama. Besides, ripping her dress off would probably have revealed the pit-viper tattoo on her navel and the death's head right above her waistline.

She waited until she saw the carriage turn around the corner and disappear down the hill. Then she rushed into the attic, almost flying over the stairs and opened her trunk. From the very bottom she pulled out the little shortwave radio and her single flare. She ran back down, into the backyard lit the flare and threw it a good twenty feet. Soon the courtyard was filled with green smoke. Then she switched on the radio and said into the mouthpiece, ``This is Cinderella calling Fairy Godmother. Come in Fairy Godmother. Over.''

After a few short seconds the radio crackled back to life and a man's gruff voice came over the air ``This is Fairy Godmother calling Cinderella, package is on the way. Where do we drop? Over.'' ``Fairy Godmother, hit the green smoke. Repeat, hit the green smoke. Over.'' And then she waited for what seemed like an eternity, but was closer to five minutes.

When she looked up into the sky she saw three stars that seemed to moving and getting larger. Behind them, she could just about make out the silhouette of white parachutes. Two of the parachutes, and the boxes they were attached to landed right in the courtyard while the third one had drifted off and landed near the pumpkin patch. Inside the first box, was a bag containing a pure black body-hugging jump suit. There was also a heavy duty Kevlar vest and a pair of thigh high combat boots. Inside the second box there were two bags. One bag contained a .44 Magnum Desert Eagle, her favorite OKC-3S bayonet knife, two more flares and extra clips for the Desert Eagle. She didn't open the second bag. She quickly pulled on the suit, vest and boots, loaded the gun and then headed off to find the third box.

The third box hadn't landed near the pumpkin patch, it had landed right in the patch and flattened one of the stepmother's prize pumpkins. Cinderella shrugged and went about opening the third box, after tonight it wouldn't matter. Inside the third box was a strapped down M1030 motorcycle also painted jet black. She was relieved to find that the gas tank was full. Some idiot had forgotten to fill the gas tank on an earlier drop and she had almost made some heads roll, literally.

Once she was all geared up, she turned on the radio again, ``This is Cinderella, all equipment is in order. I'm heading out. Any last minute instructions?''

``Roger that, Cinderella. Remember that once you have acquired the target, get to the roof and give us red smoke. If anything goes wrong, give us green smoke and we'll abort. The bird will come in at 0000 sharp. Good luck. Over.''

``Roger, Fairy Godmother. Look for smoke at 0000. Over.''

She jumped on the bike and rode off in the opposite direction from what the sisters had taken. She didn't particularly like taking the backroads, but she couldn't risk being seen, certainly not with a large black bag slung over her shoulders.

\section*{Part 2}

The last half hour drive through the forest was terrible. She was continually bumping up and down, bruising herself in the most uncomfortable places and the bag swung starting to make her shoulders hurt. She was relieved when she finally made it to the end of the forest, saw the gap in the fence surrounding the palace compound and the gardener's hut just inside the fence. She left the motorcycle carefully concealed in the trees, walked through the gap in the fence and drew her knife as she approached the hut. On the one hand she was hoping that their contact inside had done his job and cleared out the hut, but on the other hand, she was spoiling for a fight after a few weeks of washing dishes and polishing floors.

The hut was dark and door unlocked. She opened the door and looked inside, letting her eyes adjust to the darkness. The light from the palace had lit up the outside, but the hut's tiny window let little light in. After she was sure there was nothing suspicious she quickly stepped in and locked the door behind her. She placed the bag on the small table in the middle of the hut and took out of it a bundle of bright blue cloth. When she held up the bundle and let it unfurl itself, it turned out to be a gorgeous gown which caused her to promptly curse under her breath. The gown was backless and she hoped that it went down low enough to cover her death's head tattoo. In the darkness, without a mirror she had no way of knowing.

Underneath the gown was another much smaller bundle and when she unwrapped it revealed an equally gorgeous pair of glass slippers. She cursed again, this time louder. Some idiot at HQ obviously read too many comic books and thought it was possible to aim a deadly kick to the skull while wearing 4-inch stilettos. To top it off it was also a tad tight. Someone was going to pay for this treachery. She considered keeping her combat boots on, but that might give her away too easily. And besides, the slippers actually were quite beautiful.

Cinderella had been trained to go from fully clothed to naked and then suited up for combat in 2 minutes flat. But putting on a dress in the dark turned out to be quite a task and it took her almost a full twenty minutes. But like all her dangerous missions, she succeeded and put on the slippers. As she was packing her vest and boots into the bag, she noticed two more things in the bag: A diamond necklace that had probably been confiscated from some overthrown African dictator and a gilt edged invitation. They were both quite gorgeous.

After throwing her bag into the woods near her motorcycle. She headed towards the palace. Though she knew the palace and grounds plans by heart, she decided to stop and ask a guard for help. If he helped her and told her where to go, her disguise had worked. If he didn't her knife would quickly cut his jugular in half and she would go on her way, being sure to stop at a mirror first.

She was near enough to the party that when the guard saw her, she wasn't exactly shrouded in darkness.

``Excuse me, kind sir. I'm afraid I'm lost and kind find my way to the ball. Would please be so kind as to point in me in the right direction? Please sir, my mother shall be terribly worried if I don't return in time.''

It took the guard a full minute to actually say something legible and offer to take her to the palace entrance. Cinderella attributed it to the fact that the front of the dress, like the back, was also quite low cut and about half a size too small. The walk to the palace wasn't very long but Cinderella counted at least 7 times when the guard had snuck a look sideways and down. She considered drawing her knife but then decided that it was actually quite flattering. She hadn't had a chance to wear many beautiful dresses and impress young guards while she was busy snapping necks in the backstreets of Beijing.

\section*{Part 3}

When she reached the palace, there was a much older and senior guard at the door. He didn't have the younger guard's delayed response and though he seemed to just wave her in, Cinderella noticed his eyes travel up and down her body, stopping for a split second at her hips and then scanning the invitation trying to detect a forgery. He was obviously very good at what he did and for once she was happy that she didn't have to draw her knife. It would have been a terrible waste.

Once inside, the sight that greeted her was more gruesome than any battlefield she had ever seen. There were probably hundreds of pretty young things strutting about in all their empty splendor, accompanied by their doting parents. The myriad perfumes seemed to join forces and attack her nostrils as one putrid stench. And the cacophony of their hollow artificial voices was scarier than any artillery fire she had heard. It disgusted her and it took a supreme effort of will for her to not unholster her Desert Eagle and pop off a few rounds. Her job for now was to keep an eye on the Prince and she was going to do it.

Luckily for her the Prince was in plain sight, sitting on a raised platform at the far end of the room and looking really quite bored with everything going on around him. Cinderella walked down the hall toward the Prince and as she did, all eyes turned towards her and conversations stopped. For a few seconds she was afraid that the back of the dress was too low and her tattoo was on full display for everyone to see. But she rationalized that if that was the cause, one of spoiled young oh-so-civilized brats in the room would have shouted it out by now. The fact that they hadn't probably meant that they were just staring for no other reason than that she was worth staring at. Despite herself, her face broke into a small smile.

By the time he reached the platform, even the Prince had taken notice of her. As she curtsied somewhat awkwardly he did what he had been wanting to do for the whole time: He stepped of the platform and stood right in front of her. Cinderella got up from the curtsy and looked right into the Prince's eyes. She saw in his eyes the same thing she had seen in so many eyes every since Tommy Bean had told her in fifth grade: `` You're pretty. Wanna be my girlfriend?'' She had answered Tommy Bean with a punch to the face (and never got in trouble because no one believed a girl had hit him) but this time, all she did was take the Prince's hand when he offered it. Damn it, she thought to herself, not again.

As they danced a whole slew of thoughts went threw her mind. At first she cursed her luck, the low cut dress and whichever poor bastard she was going to kick between the legs when she got back to HQ. Then she thought that maybe it wasn't too bad after all, since she was right next to the Prince like she was supposed to be. As she turned in the steps of the dance she swept the ballroom for any signs of danger. About half an hour in, she saw her target: a thin balding man, dressed in almost regal robes who always seemed to stay just on the edge of the main party. She alternated sweeps of the ballroom with keeping an eye on the man. After she had sunk into a comfortable routine she actually started to notice the Prince. He was quite tall, a few inches more than her even with her stilettos. And he was certainly good looking, probably one of the best looking men she had ever gotten close to. Except perhaps for the Sultan's son, but he had been a genocidal maniac and she had put a bullet in his head, so he didn't really count. If she was the real Cinderella, she wouldn't be bothering with all his dancing about in a pretty dress business, but would have gotten straight to the point. As for the Prince, the only thought he felt capable of thinking was: ``This is the girl for me.''

As midnight drew nearer, Cinderella was starting to get worried. If the man didn't make a move, there was nothing she could do either. If he kept up his inactivity much longer she would have to stick around until he did do something and that would mean missing her pickup. She had done it before on a few occasions and it was not something she enjoyed.

The Prince didn't talk very much, they never did at first and after almost an hour the only thing he could say was, ``What is your name, fine lady?''. Cinderella was just about to give her full cover story when she noticed the balding man quietly slip out of the ballroom and disappeared through one of the side doors. She had to follow him and all she could muster in a split second was ``I'm sorry my Prince, but I really must go.'' And as she broke his hold and started walking in the man's direction, she turned for a second and said, ``It would be best if you forgot about me.'' She never understood why she said that.

\section*{Part 4}

Cinderella walked quickly to the door through which the man had disappeared, trying hard to ignore both the stares of the people around her and the Prince asking her to come back. The door opened into a corridor which itself seemed to be a side exit to the grounds outside. But off to the side was a winding staircase and after listening for a second, she clearing heard the sound of a man's boots coming from the stairs. Cinderella drew her knife and started climbing the stairs. But after just a few steps one of her slippers slipped off and tumbled down the stairs behind her. Climbing the stairs with only one slipper on was uncomfortable, but she didn't dare stop to take it off. For all she knew the man had a gun trained on her and the second she stopped their would be a bullet in her head.

At the top of the stairs she found herself in front of a locked door. She steadied herself on her bare foot and used the other one to kick open the door. Behind the door was a small dark room, with a single window looking out onto the ballroom below. Through the light coming in through the door she saw the man she had been chasing with a gun in his hand. The gun was pointed straight at her head.

``Well well, what do we have here? Come to save your beloved Prince have you?''

``Actually, I just came for you, Prime Minister. Saving the Prince was a completely unintentional consequence.''

``Very funny. Unfortunately, I can't shoot the Prince in the ballroom as I had hoped, but once I shoot you, your Prince will hear the shot and come rushing up the stairs, standing right where you are now.''

Cinderella silently cursed herself for falling into such an obvious trap. She was still standing in the darkness. Though she couldn't count on the Prime Minister to miss her at this range. He had probably not noticed the knife in her hand. All she needed was a little distraction. After a few seconds of deathly silence, the Prince's loud voice came up from the bottom of the stairs, calling up after her. For a fraction of a second the Prime Minister's attention shifted and that was all the time she needed. She threw the knife into his shoulder, severing the tendons and nerves he would have needed to pull the trigger. In another second she had moved two steps forward, steadied herself on her bare foot and landed a strong kick against the Minister's skull. He crumpled to the ground, the gun still clutched in his hand.

She went back to the door and pulled it shut. She considered running back down and retrieving the slipping, but she couldn't risk being seen by the Prince. Instead she looked around the room and quickly found what she was looking for. In the far corner of the room was a small ladder leading up to a trapdoor in the ceiling. Opening the trapdoor she found herself looking out on to the roof, the plans she was given had been quite accurate. She pulled out one of the flares that she had tucked into her dress, lit it and threw it onto the roof. She then grabbed the Minister's limp body and dragged it up behind her onto the roof. Once she had securely placed herself on the roof, she closed the trapdoor and waited. Hopefully her ride would arrive soon before the guards noticed the smoke from the flare.

\section*{Part 5}

As she heard bells in the Palace ringing in the arrival of midnight, Cinderella looked up to sky and saw the familiar site of a Blackhawk chopper descending down to where she had thrown the flare. Once it was low enough a man jumped out of it and landed expertly on the roof -- a man who looked exactly like the incapacitated Prime Minister. He nodded to Cinderella and proceeded to open the trapdoor and climb down. Cinderella thought it was a bit much to have two look-alikes on the same mission, but decided that it was really none of her business. Another man reached out from inside the Blackhawk and helped pull in the Minister. As soon as Cinderella was in herself, the chopper took off.

``Good work, Agent Cinderella. I see you didn't make much of a mess this time.'' said the man who was probably as old as the Prime Minister, but a bit on the heavy side.

``Thank you, Fairy Godmother. Though I might have a bit of a mess to make at Equipment once we get back to HQ.''

``Oh, Equipment. Yes, I think they have a new guy. Try not to paralize this one.''

It wasn't until the Blackhawk had stopped ascending that Cinderella noticed that there was someone else with them. In the darkness all she could tell was that it was a girl huddled into a corner. She nodded in the girl's direction and asked the Godmother ``I didn't know we brought civilians on missions''.

``Oh, I almost forgot. Cinderella meet Ella. We're dropping her off at her house. Part of cleanup.''

Cinderella took a closer look at the girl. In what little light came through the windows, she saw that Ella did in fact look a lot like her. They were both lightly built, about the same height and had shoulder length blond hair. It wasn't too hard to see why she had managed to fool her stepmother and stepsisters for so long. They both stared at each other for a while before Cinderella said ``Hi.''

``Please don't send me back to my horrid stepmother and stepsisters. They'll only make me sweep the floors and do the dishes all the time. Can't you just let me go somewhere else?''

``I'm sorry, but it doesn't work that. People would ask too many questions.''

``You saved the Prince didn't you? They told me he was in trouble and that they were sending someone to save him. Did you get to actually meet him?''

``Yes, I danced with him.''

``Danced with him? You actually \textit{danced} with the Prince himself? Oh.... What was he like? Was he tall and handsome like in all the pictures?''

Cinderella could tell that the poor thing was absolutely smitten by this man, even though she had never seen him in her life. She was about to tell her not to be so naive, but instead just said ``Yes, he was tall and handsome.''

``Oh, my. I so wish I could see him just once.'' Ella didn't say much else after that until the pilot called out, ``We're almost at the house, you'd better get ready.''

At this Ella seemed to wake up from her reverie and said again, ``Please don't send me back.''

Despite herself Cinderella found herself saying, ``Look calm down would you? The only way you'll get a better life is if you start standing up for yourself. I know how they treat you and it isn't nice, but only you can change that.  And besides, everyone thinks you were at the ball and if your Prince is as brave and handsome as you make him out to be, he'll come looking for you, so don't worry.''

``I was at the ball? But, but ... I wasn't, \textit{you} were. What should I do if they ask me? What should I tell if the Prince comes and asks?''

``Tell them... Tell them a Fairy Godmother helped you out. Gave you a dress and a ride. And tell them you had to leave by midnight or else something bad would happen.... the magic would go away.''

For some reason Ella didn't seem to complain at this. Silly girl, Cinderella thought, but she found herself pitying her anyway. As the chopper landed and Ella was getting out Cinderella called after her, ``Wait, take this. It might come in handy.'' She took the remaining slipper off her foot and handed it to Ella. Much to her surprise it wasn't broken or even cracked. She looked sideways at Fairy Godmother who seemed to be doing his best to ignore the whole thing. Ella's eyes lit up as she saw the slipper, she had never seen anything quite so beautiful. As the Blackhawk lifted up, she said to herself, ``Thank you, Fairy Godmother.''

\section*{Epilogue}
The rest, as they say, is history. The Prime Minister's replacement managed to keep a close eye on the Prince and prevented him from doing anything stupid during his reign. As for the Prince, he did find the glass slipper that Cinderella lost and promptly launched a search for her across the kingdom. Since Ella had the other slipper and because she looked so much like Cinderella, no one doubted that it was her the Prince had danced with. Ella, for her part, took Cinderella's suggestion about a Fairy Godmother, added mice, horses and a carriage made from the crushed pumpkin that she had to clean up the next morning. She married the Prince and they lived happily ever after. 

Cinderella would keep on snapping necks and putting bullets in brains for years to come.  Then one fine day she decided she was bored of it all and quit. Her current whereabouts are classified beyond Top Secret.

The End.

\end{document}
