\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, fullpage, pslatex}

\title{Bells}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle
\doublespacing

The bells started to toll somewhere far away. It was Sunday, people were going to church. But not he. He was sitting by the window, looking up at the cloudy sky. He thought that it was apt, that he heard bells this morning, that the sky was dull and unremarkable. It seemed to reflect his life, his life which would soon end.

His father had been a blacksmith and his grandfather had helped make the church-bells in his home town. Then one day his father left to join his mother in Heaven. An uncle that he had never seen turned up and claimed the family business. he lived with his uncle a while, but soon he had to leave the heat of the blacksmith's forge for the cold of the street. In a way it was a good deal, he had traded in his uncle's oppression for the wide world.

For a while he imitated sea-weed, drifting from place to place. Then he got caught up in that great whirlpool of humanity, London. It had all gone downstream from there. He tried doing odd jobs, running errands cleaning coaches, he even cleaned the church bells for a month. But there was always someone who did what you did, better and cheaper. In the end he stopped working altogether.

He tried to steal a few apples from a small wedding. He'd picked the ringing of the marriage bells as the right moment. He was wrong. He didn't get apples, he got thirty lashes. He hated bells from then on, right to last month, when he killed the coachman who almost ran him over. It wasn't his fault, the driver came around a corner, horses almost at a gallop and he didn't have the required bell that warned pedestrians of speeding coaches.

He had never studied law, but he liked the legal system, it had been fast. He had been convicted in two days and was due to die a week later.

The warden unlocked the door. He went out onto the gallows. There was a small crowd, he didn't care. As the cloth went over his head, he heard church bells again. He had asked for a Sunday, without really knowing why. The rope went around his neck. He didn't have money for a funeral. There would be no more bells for him. 

\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}
\end{document}