\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, fullpage, pslatex}

\title{Guardian Demon}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle
\doublespacing

I should never have been born and my mother should never have died. At 30 weeks there was a greater than 50\% chance that I would die soon after I was born. My mother, who had been sick throughout the pregnancy, would not have survived the trauma of a premature birth. The doctor advised her to give me up so that she could live. In retrospect, I agree with him. But somewhere along the line an intern messed up. A few hours later my mother was dead and I was alive, my lungs barely breathing and my heart barely beating, but alive.

I don't think my father ever quite forgave me for being born. But for most of the time I knew him, I was too young to care. For all intents and purposes he was an alcoholic. I have memories from the time when I was about four or maybe five. He would leave me with a babysitter every weekend. A different one each weekend because anyone who was around when he got back didn't want to be there a second time. He would come back in the early hours of the morning, waking me up more often than not. He'd call me a ``devil child'', saying that I'd killed my mother and was plotting to kill him too. He'd call the babysitter a whore and a bitch and say things along the lines of, ``You can stop suckling the devil child now'' or ``Don't get too close to the devil child if you want to live''. I think at the time I didn't quite understand what he was saying, but I remember the babysitters being very angry and upset and generally storming out of the house.

On the night of my sixth birthday my father was out drinking as usual. The babysitter was a girl from down the street called Julie. My father came back at some point in a drunk stupor but hadn't started on his tirade about me yet. Julie thought that it was horribly unfair that I had been left alone on my birthday. She told my father exactly how she felt, ``Mr. Allen, I don't think it's fair to Bill to be sitting all alone at home on his birthday. And I don't think it's right for his father to be out getting himself drunk on his...''. She never finished her sentence because at this point my father had struck her on the cheek and knocked her to the ground. My father wasn't a violent man as such, but I think the suggestion that he actually spend time with the person responsible for his wife's death was too much for him to take.

``Feel bad for the devil child, do you, you little bitch? What's he paying you to fuck around with me? Or does he just make everyone he meets into his personal whore?''

It was at this point that he actually saw me standing just behind the door to the kitchen. ``Stand and watch will you, you little bastard? Want me to kill her like you killed your mom? Is that what you want? Answer me, when I talk to you!''

I didn't say anything. When I saw him stumble towards me, leaving a sobbing Julie on the floor, I ran back into the kitchen, behind the kitchen table and as far into the corner as I could go. When he finally managed to stumble through the door, it took him a few seconds before he actually saw me. For just a second our eyes met. I think it was the only time we had ever actually looked into each others' eyes. He looked around him and eventually picked up one of the knives from the knifestand near the door. I never figured out why they were there, especially since my father never cooked.

He came for me again, with the knife in his hand, but in his drunken state the kitchen table was a significant obstacle. As he stumbled around the table he knocked off a mug of cold coffee that had been sitting there since morning. The coffee made a puddle beside the table and it was on this puddle that he slipped and fell. As he fell, his head struck the corner of the table with a loud crack and once he hit the ground, he didn't get up again.

I don't know how long I stood in the corner, but I remember that at some point Julie came into the room, her face red from crying and partially covered by her hair. She took one look at my father's body on the floor, the pools of coffee and blood now mixing and ran out again screaming. A while later she came in again, grabbed my arm and pulled me out of the kitchen. The police came soon after and the last time I saw my father was when his body was put in a black bag and taken away.

My first foster home wasn't really bad at all. My foster parents weren't the most loving kind, but didn't hurt or scare me either. School, however, was a different matter. The world of children is a quite cruel and unforgiving one. There are always other kids out to hurt you and once something bad about you gets out, it's practically impossible to live it down. Somehow word at school got out that both my parents were dead under less than innocent circumstances. It may just have been rumor in the vicious way that children's rumor generally is, but the effects were the same. Tables around me at the dining hall immediately started clearing out. The other kids were careful to form playgroups that didn't include me and the teachers generally turned a blind eye.

Worst of all were the bullies. There was this one kid, Frank, who was heartless in the way that only young children can be. At some point he got tired of making fun of the kids with glasses and decided to turn his attention to the kid who had killed his parents instead. With his band of boys he took particular care to make sure that my life was worse than what it had been before. They sat next to me at meals, but only so that they make fun of me and spit on my food. They played with me during breaks where their favorite game was ``Punish the murderer''. The usual series of bruises and black eyes followed, but I was always a timid, quiet child and became quite skilled at avoiding my foster parents questions. The last thing I needed was to get Frank in trouble and then have him take out his revenge on me.

But find out they did and as expected Frank got in trouble. Also as expected he cornered me the next day in the playground behind the school building.

``So you think you could go running to your mommy did you? Oh no, you can't 'coz you already killed her didn't you? What's wrong you little twerp, too stupid to talk? I bet that's why your folks died, couldn't stand having a stupid twerp like you as their kid.''

I talked a bit more by that time than when my father had come down on me, but even then all that I could muster was a feeble  ``Leave me alone''.

``I'll leave you alone, once I break your ugly twerp face.''

I had learned to realize the signs of a coming group beating and I could tell that this one was going to be worse than any of the other ones, and so like any 7 year old, I ran. The playground ended in a rocky patch with a tall fence behind it. I ran over the rocks as best I could and started clambering up the fence. I didn't dare look behind me because I could hear Frank and his gang right and I was afraid if I turned I would only see Frank right on top of me.

As I got near the top of the fence I felt something pull at my leg. Looking down I saw that Frank had climbed the fence behind me and was trying to drag me down. I hung on to the fence for dear life while trying to kick Frank away. But he was larger and stronger than I was and was starting to come further up while pulling me down. He managed to climb up to the point where his face was just within reach of my foot. I kicked out and felt my foot make contact with something hard, which then gave way a split second later. I heard Frank give one of the most terrible yells I ever heard, felt him let go of me and a second later I heard him scream even louder as he hit the ground. Behind me I heard his gang go from cheering him on to silence and then more screams which gradually died away. I guess they must have run away, back to the school building. For my part I was too scared to even move and just hung on to the fence.

It took a policeman to come and get me down from the fence because I wouldn't let go. I thought Frank, like my father, was dead. I later learned that he survived but had snapped his spine on the rocks and would never walk again. I was quickly moved to another school where I was careful never to mention Frank accident or my parents' deaths.


When I was ten I moved to my second foster family. I hoped that this move would let me make a fresh start. Things were going pretty well for a few years until I met Uncle Joey. Obviously, Joey wasn't really my Uncle and he wasn't even related to my foster parents. But everyone called him Uncle Joey. At thirteen I was a scrawny teenager and probably looked more like ten or eleven. Perhaps that's why Uncle Joey started coming to our house more and more.

It started by him insisting on taking me to my swimming lessons and then sitting by the pool to make sure that I didn't ``hurt myself''. He'd run his fingers through my hair and up and down my back to make sure that I'd dried myself properly. As the weeks went by, his interest in whether or not I had ``dried myself'' went beyond my back and extended to my arms and legs.

Uncle Joey was a photographer. I was just starting to notice girls and Uncle Joey would bring me pictures of girls asking things like, ``You think she's pretty?'' or ``Don't you just wish you had a girlfriend like her.'' We shared a few laughs after swimming lessons, but it started getting less appealing when he began bringing more pictures of boys than he did of girls.

One day Uncle Joey brought me home after swimming. I was in the bathtub, taking a shower when I heard the door to the bathroom open and Uncle Joey.

``Uncle Joey, I'm in here.''

``Yes I know. Don't mind me, I'm just going to take a few pictures.'' He pulled back the curtain. I stood there naked and more than a little confused. I had thought that it was a little weird that he took pictures of boys but I didn't think he would want to take pictures of me.

``Uncle Joey, I don't like this.''

``What's the matter? You like looking at those pictures, what's the matter with being in one? And besides, you wouldn't want me to have to tell your parents you've been looking at pictures of girls, would  you?''

One of the other boys in the house had gotten in trouble a few days earlier for having an adult magazine tucked under his pillow and I knew my foster parents would believe whatever Uncle Joey said. I was still uncomfortable but didn't want to give him a flat no. I got out of the tub and said, ``I'm actually done showering, so I'll just dry myself off.''

``Yes, yes, do that. But don't rush with it, you need to dry yourself well.''

I tried to keep my back to him as I dried myself with the camera flash periodically filling the room with light. After the fourth or fifth picture, he told me to turn around so that he could ``get a better view''. As I turned reluctantly, he put his foot up on the edge of the bathtub, rested his elbow on his knee and prepared to take a shot. But right before his finger pressed down on the trigger, he slipped and fell sideways into the the tub. We had been having drainage problems and the plumber hadn't fixed everything yet. Uncle Joey splashed into the foot or so of standing water and I saw the flash go off. I also a heard a sizzling sound and watched as his body convulsed involuntarily for a few seconds and then become motionless.

This time, there was actually an investigation and for a while I was a suspect. But it turned out that the camera flash had a faulty capacitor and as Uncle Joey's photo collection became public knowledge, the only thing that happened to me was getting moved to yet another foster home.


I met my first girlfriend in my sophomore year of high school. Her name was Claire and we were madly in love. When I was with her, I wished time would stop so that I didn't have to do anything else or go anywhere. I've never felt about anyone else what I felt for her. But good things never last and we broke up a month into Junior year.

A week after we broke up I found myself at a party at a friends house. Actually, saying he was a friend is a bit of stretch. He was more of an acquaintance, but he had rich parents who were out of town a lot leaving him alone in a big house. He had some older friend who went to the local community college, so at his parties the beer always flowed like water. That night I found myself drinking it like water. There was this other girl there who I knew went to my high school. I didn't really know anything about her except that her name was Sally. But I thought she was pretty and now that I didn't have a girlfriend anymore, I thought I'd take my chances. Everything after that is a bit of a blur. I guess the beer was working.

I remembered waking up the next day in my acquaintance's bed with a splitting headache and Sally next to me. I don't think we were wearing any clothes. After the weekend I was back at school, fishing around in my locker for books for next class. As I closed my locker and turned around, I saw Sally standing there right behind me. I could only mutter a weak ``Hi, Sally'' before she cut me off and said, ``You bastard! How you could you?''

``What? How could I what?''

``You know what. The other night at Mike's place. You got me all drunk and then you... you... raped me.''

``What the fuck are you talking about? You were already drunk when I met you and... ''

``And that makes it alright? You're going to pay for this. I'll make sure you never touch anyone again.''

``Hey Sally, hey wait a minute...''

But she had already turned around and was practically running down the corridor away from me. I hadn't been that scared for a long time. I was afraid she would tell the Principal and get me expelled or worse yet, go to the police and file charges. For the whole day I sleepwalked through my classes and didn't really pay attention to anything. At home I didn't eat and locked myself in my room.

The next day when I came down to the table, I saw my foster father sitting at the table with the local paper open in front of him. The first headline read ``Mother and daughter killed in car crash''. As I sat down at the table my foster mother said, ``Oh, did you hear what happened? Some poor girl from your school was in the car crash with her mother. Sally, Sally Mitchell. Did you know her?''

``Umm.. no, mum. Not really.''

``Oh it's so sad when young people have to die. And it was right in front of the police station too.''


As I went through high school, I realized that things weren't quite normal with me. I started doing pot, but the idiot who supplied me got caught and ratted me out to the Principal. He was going to tell the cops. That night the Principal was killed in an armed robbery at his local grocery store. 

I started dating this girl who one of the football players had a crush on. One day he cornered me in one of the stairwells, punched me in the face and kicked me in stomach. As the bell rang, he told me he'd finish it after school. When school finished and I headed out, hoping to be able to get home with all bones intact, I heard he had broken his neck during practice. After a few more incidents I started realizing that I was, for all intents and purposes, practically untouchable.

Other people might have there guardian angels, I have my guardian demon. If I was a God-fearing person, I would be scared right now. But the way I see it, God has been looking the other way all the time. My Demon takes care of me and I'm starting to like it. I know people are getting hurt but they deserve it, every single one of them. At the end of it, does it even matter? People die all the time and become no more than statistics in a book, quickly forgotten. But I live and that's good enough for me.

\end{document}