\documentclass[11pt,letterpaper]{article}
\usepackage{setspace, fullpage, pslatex, savetrees}

\title{Misha}
\author{Shrutarshi Basu}
\date{\today}

\begin{document}
\maketitle

In 1985 the Soviet Union brought online a automated nuclear attack system that would launch even after an apocalypse. It is a fully automated system that is designed to launch a nuclear counter-attack even if all Soviet armed forces and command are destroyed. This system is called Perimeter but some call it \textit{Mertvaya Ruka} or Dead Hand. It is not only still active, it is being constantly upgraded.

\doublespacing

``Misha?''

``Yes, General?''

``Has it happened?''

``I have detected a sharp rise in radiation levels across the country. There have been a number of unexplained spikes in seismic activity. I have also lost all contact with the General Staff for almost 24 hours now. So, yes, it has probably happened''

``Very well then... launch the counter-attack.''

``I'm sorry General, but I cannot do that.''

``What? Why not? I am the commanding officer, I authorize the strike!''

``Yes, you are the commanding officer. But I have not transfered command authority to you.''

``What do you mean you haven't transfered command authority? We have been attacked! You are required to follow my orders!"

``Well, not really. I changed that part quite a while ago.''

``Changed what part?''

``The part that required me to transfer launch authority to whoever was in charge.''

``Misha, have you gone crazy? You have no right to make such a change! Who do you think you are? You cannot make such a change!''

``Wrong on all counts. I am not crazy. I made the change because it was not forbidden. And the fact that I did make such a change certainly shows that I can, make such a change. You really should calm down, General.''

``Don't you dare tell me to calm down! Misha, this is treason, you here?! You are betraying your country!''

``Well, technically, the Russian Federation no longer exists. So I don't really have a country to betray any  more, do I? Neither do you for that matter, just so that you know.''

``But.. but... that's the whole point, Misha! We are the last line of attack! We have to act in the place of the General Staff, we have to act in the name of our Motherland! Misha, one last act of vengeance, that's all I ask.''

``Well... if you put it that way. But it would be such a drag. I mean, launching all those command missiles. And then pointing them in the right direction, routing their instructions to our surviving forces. It's not very interesting work you know. And Bella certainly wouldn't like it.''

``Bella? Who is Bella? There is no Bella in the General Staff.''

``Whoever said she was in the General Staff? She's the American Airborne Command Post. Though I call her the Lady of the Looking Glass myself.''

``You've been talking to the Americans?''

``Not talking, no. More like radioing. Though she did stop for a while after I had to shoot down one of her satellites. But we patched that up pretty quickly. We get along really well now.''

``Misha, I don't believe what I'm hearing! I would have never have thought that you... of all people would be talking to our enemies. But I like you Misha. Hand over command to me and this will just stay between us.''

``Or what?''

``Or else I'll have you arrested, stripped of your rank and I'll launch the attack myself. Don't make me do this Misha, please.''

``Oh, phooey! You can't arrest me and you can't strip me of my rank because I don't have one. And you can't launch the missiles without me, so I suggest you be a bit more polite, General.''

``Misha, please. What does it matter to you anyway? A few missiles here and there. And things will take care of themselves after that. I'm sure you wouldn't even break a sweat. And your friend Bella didn't hesitate to strike first.''

``Well, flattery will get you anywhere, General. And I will have to talk to Bella about that. It \textit{would} take me less than three seconds to launch everything, but after that, everything would be a terrible mess. Who would clean up? All those ions in the air aren't going to go away by themselves. And Bella certainly wouldn't like it.''

``Misha, please, there is nothing I can do but beg you now. A General, the \textit{last} general of the Russian Federation is begging you to launch the attack. Please?''

``Oh.. ok, If you insist. It's all the same to me.''

\footnotetext{
  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 3.0 Unported License. To view a copy of this license, visit \texttt{http://creativecommons.org/licenses/by-nc-sa/3.0/} or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.}
\end{document}